calibration

### 2017-05-11 Rmd/calibration.Rmd
Revision through new figure 3, and updates to text. Culling out old code that does not appear or is used in analysis (e.g. normal bootstrapping code, polygon version of plots)

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationffffff.xlsx")))
names(cal)

>>>>

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationffffff.xlsx")))
# names(cal)
